Composable Generalized Consensus

### 2015-11-10 paper/intro.tex
Added two new references.

Making SMR algorithms efficient has been a long-standing challenge
and a multitude of algorithms have been proposed. Examples include
Paxos \cite{lamport2001paxos}, Fast Paxos \cite{Lamport06FastPaxos},
Disk Paxos \cite{GafniLamport03DiskPaxos}, Chain Replication
\cite{RenesseSchneider04ChainReplicationSupportingHighThroughputAvailability},
Ring Paxos \cite{MarandiETAL10RingPaxosHighthroughputAtomicBroadcastProtocol},
Egalitarian Paxos
\cite{MoraruAndersenKaminsky13ThereIsMoreConsensusEgalitarianParliaments},
Multi-Coordinated Paxos \cite{CamargosSchmidtPedone07MulticoordinatedPaxos},
Cheap Paxos \cite{LamportMassa04CheapPaxos}, Vertical Paxos
\cite{LamportMalkhiZhou09VerticalPaxosPrimarybackupReplication}, Paxos-MIC
\cite{HurfinMoiseNarzul11AdaptiveFastPaxosMakingQuickEverlasting}, Mencius
\cite{MaoJunqueiraMarzullo08MenciusBuildingEfficientReplicatedStateMachine},
Fast Mencius \cite{WeiETAL13FastMenciusMenciusLowCommitLatency},
the Chandra-Toueg algorithm
\cite{ChandraToueg96UnreliableFailureDetectorsReliableDistributedSystems}, the
Ben-Or algorithm \cite{BenOr83AnotherAdvantageFreeChoiceCompletelyAsynchronous},
and Raft \cite{OngaroOusterhout14SearchUnderstandableConsensusAlgorithm}.

>>>>

Making SMR algorithms efficient has been a long-standing challenge
and a multitude of algorithms have been proposed. Examples include
Paxos \cite{lamport2001paxos}, Fast Paxos \cite{Lamport06FastPaxos},
Disk Paxos \cite{GafniLamport03DiskPaxos}, Generalized Paxos \cite{Lamport05GeneralizeConsensus}, FGGC \cite{SutraShapiro11FastGenuineGeneralizedConsensus}, Chain Replication
\cite{RenesseSchneider04ChainReplicationSupportingHighThroughputAvailability},
Ring Paxos \cite{MarandiETAL10RingPaxosHighthroughputAtomicBroadcastProtocol},
Egalitarian Paxos
\cite{MoraruAndersenKaminsky13ThereIsMoreConsensusEgalitarianParliaments},
Multi-Coordinated Paxos \cite{CamargosSchmidtPedone07MulticoordinatedPaxos},
Cheap Paxos \cite{LamportMassa04CheapPaxos}, Vertical Paxos
\cite{LamportMalkhiZhou09VerticalPaxosPrimarybackupReplication}, Paxos-MIC
\cite{HurfinMoiseNarzul11AdaptiveFastPaxosMakingQuickEverlasting}, Mencius
\cite{MaoJunqueiraMarzullo08MenciusBuildingEfficientReplicatedStateMachine},
Fast Mencius \cite{WeiETAL13FastMenciusMenciusLowCommitLatency},
the Chandra-Toueg algorithm
\cite{ChandraToueg96UnreliableFailureDetectorsReliableDistributedSystems}, the
Ben-Or algorithm \cite{BenOr83AnotherAdvantageFreeChoiceCompletelyAsynchronous},
and Raft \cite{OngaroOusterhout14SearchUnderstandableConsensusAlgorithm}.
